Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from biclaR

### 2024-05-06 paper/PaperCEUS/PaperCEUS_rev1.Rmd
review percentages bikeper conditional

# re-calculating the percentage of trips
CAR_PT_TRANSF_mun_or_geo_18 = CAR_PT_TRANSF_mun_or_geo_18 |> 
  left_join(TRIPSall_mun, by = c("Concelho" = "Origem")) |>

  #CONTINUE FROM HERE ---  LOOK AT DIFRERENCES TOTAL AND VIAGENS

mutate(Car_4 = Car - Bike_new4,
         Car_10 = Car - Bike_new10,
         TP_4 = TP + Bike_new4,
         TP_10 = TP + Bike_new10,)

@@

# plot 2
ggplot(data = CAR_PT_TRANSF_mun_or_geo_18) +
  geom_sf(aes(fill = TP_10per)) +
  viridis::scale_fill_viridis(option = "G", direction = -1, name = "Bike + PT trips %", na.value = "white") +
  theme_void()
  # theme(legend.position = "bottom") +
  # labs(title = "Potential Bike + PT for 10% target, by municipality")

>>>>

# re-calculating the percentage of trips
CAR_PT_TRANSF_mun_or_geo_18 = CAR_PT_TRANSF_mun_or_geo_18 |> 
  left_join(TRIPSall_mun, by = c("Concelho" = "Origem"))

  #CONTINUE FROM HERE ---  LOOK AT DIFRERENCES TOTAL AND VIAGENS
ENMAC4 = 0.04 # 4%
ENMAC10 = 0.10 # 10#
CAR_PT_TRANSF_mun_or_geo_18 = CAR_PT_TRANSF_mun_or_geo_18 |> 
  mutate(Bikeper = Bike / viagens) |>  #should it be "viagens" or "Total  -- all trips, not only the found ones
  mutate(Bike_new4 = ifelse(Bikeper >= ENMAC4*100, Bike, ENMAC4 * viagens),
         Bike_new10 = ifelse(Bikeper >= ENMAC10*100, Bike, ENMAC10 * viagens)) |> 
  mutate(Bike4 = ifelse(Bikeper >= ENMAC4*100, Bike, Bike + Bike_new4),
         Bike10 = ifelse(Bikeper >= ENMAC10*100, Bike, Bike + Bike_new10),
         Car_4 = ifelse(Bikeper >= ENMAC4*100, Car, Car - Bike_new4),
         Car_10 = ifelse(Bikeper >= ENMAC10*100, Car, Car - Bike_new10),
         TP_4 = TP + Bike_new4,
         TP_10 = TP + Bike_new10) |> 
  mutate(Bike_new4per = 100*Bike_new4 / viagens,
         Bike_new10per = 100*Bike_new10 / viagens,
         TPper = 100*TP / viagens,
         TP_4per = 100*TP_4 / viagens,
         TP_10per = 100*TP_10 / viagens)

@@

# plot 2 - the total % of potential bike + TP trips
ggplot(data = CAR_PT_TRANSF_mun_or_geo_18) +
  geom_sf(aes(fill = TP_10per)) +
  viridis::scale_fill_viridis(option = "G", direction = -1, name = "Bike + PT trips %", na.value = "white") +
  theme_void()

# plot 3 - the added % of potential bike + TP trips - doesn't make sense to show
ggplot(data = CAR_PT_TRANSF_mun_or_geo_18) +
  geom_sf(aes(fill = Bike_new10per)) + #???
  viridis::scale_fill_viridis(option = "G", direction = -1, name = "new Bike + PT trips %", na.value = "white") +
  theme_void()
